Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
soem edits to 4 and 5

\bo{Should note that the program's solution does give candidates $\T$, although their usefulness is unclear...}
\bo{Actually, I guess one could run this, then use monotonicity to add constraints and find the next subgradient sets, etc.}

@@

\bo{Am assuming that we will have to move almost everything to the appendix, wrote this blurb instead.}\jessie{Looks good to me.}
We have two proofs, both delegated to the appendix.
The first proof is a direct geometric one utilizing the same observations.
We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome embeddings).

The second is to directly obtain from mathematical software that the program is infeasible.
We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
This reduces the quadratic program to the following problem: 
\begin{quotation}
  Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?
\end{quotation}

>>>>

@@

We have two proofs, both delegated to the appendix.
The first proof is a direct geometric one utilizing the same observations.
We show that packing too many normal vectors into a half-circle yields contradictions, implying that a $5$-outcome embedding into $2$ dimensions is impossible (and incidentally characterizing the structure of all possible $4$-outcome embeddings).
The second is to directly obtain from mathematical software that the program is infeasible.
We use observations about $\ell_{1/2}$ to make a number of simplifications to the program first.
This reduces the quadratic program to the problem: 
\emph{Given a real-valued matrix $M$ in which some entries are missing, but have bounds of the form $[a,b]$, do there exist legal values for these entries such that $M$ is rank $d$?}
